Enhancing Data Visualization: Insights from Graphical Perception and Comparative Analysis of Charts

### 2024-11-25 index.qmd
references and new lines

Following William Playfair's introduction of the pie [@playfair1801statistical] and bar chart [@playfairCommercialPoliticalAtlas1801], there were several discussions on its use and assessment.
Von Huhn concludes that bar charts are much more useful and efficient in the majority of situations, even though pie charts have specific applications.
Bar charts are often better for the majority of practical purposes, although pie charts may occasionally match or surpass them in certain situations, according to Frederick E. Croxton and Roy E. Stryker, who made this statement later in 1927.
This study will attempt to determine if pie charts may be completely disregarded in this new era or whether there are still some fields in which they can be more beneficial than bar charts.

@@

>>>>

Following William Playfair's introduction of the pie [@playfair1801statistical] and bar chart [@playfairCommercialPoliticalAtlas1801], there were several discussions on its use and assessment.
@vonhuhnFurtherStudiesGraphic1927 concludes that bar charts are much more useful and efficient in the majority of situations, even though pie charts have specific applications.
Bar charts are often better for the majority of practical purposes, although pie charts may occasionally match or surpass them in certain situations [@croxtonBarChartsCircle1927].
This study will attempt to determine if pie charts may be completely disregarded in this new era or whether there are still some fields in which they can be more beneficial than bar charts.

@@

# References
